{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-04-30 bmvc_review.tex
Some More Updates Done - Figure for UAV123_10fps Dataset Added

%\begin{figure}
%        \begin{subfigure}{0.5\textwidth}
%                \includegraphics[width=\linewidth]{./figures/Precision_UAV123.pdf}
%        \end{subfigure}%
%        \begin{subfigure}{0.5\textwidth}
%                \includegraphics[width=\linewidth]{./figures/Success_UAV123.pdf}
%        \end{subfigure}%
%        \caption{Evaluation and comparison of the proposed E$n$KCF tracker on the UAV123 dataset. UAV123 Dataset consists of $123$ video sequences captured from a micro UAV including large camera motion, low resolution objects, partial and full occlusions. Our tracker better fits to tracking from aerial platforms as the scale change in successive frames are not dramatic.}\label{fig:UAV123_DATASET}
%\end{figure}
%
%\begin{figure}
%        \begin{subfigure}{0.5\textwidth}
%                \includegraphics[width=\linewidth]{./figures/Precision_OTB100.pdf}
%        \end{subfigure}%
%        \begin{subfigure}{0.5\textwidth}
%                \includegraphics[width=\linewidth]{./figures/Success_OTB100.pdf}
%        \end{subfigure}%
%        \caption{Evaluation and comparison of the proposed E$n$KCF tracker on the OTB100 dataset. OTB100 dataset consists of $100$ video sequences of different objects from recent literatures. }\label{fig:OTB100_DATASET}
%\end{figure}

@@

\textbf{Overall Performance on UAV123$\_$10fps Dataset.}

>>>>

@@

\textbf{Overall Performance on UAV123$\_$10fps Dataset.} We test our slightly modified version of the 
{\it E}nKCF, {\it E}nKCF2, on the UAV123$\_$10fps dataset. This dataset is downsampled at $10$ fps version 
of the UAV123 dataset. The original dataset is already dominated by fast object motion and large ego-motion. With downsampling, 
it becomes very challenging with object and ego-motion getting drastically larger. The performance of the proposed {\it E}nKCF2 tracker
and other already mentioned trackers can be seen in fig.~\ref{fig:UAV123_10fpsDATASET}. Our tracker outperforms other high-speed correlation filter based 
trackers including KCF, DSST by about $15\%$-$20\%$ whereas having similar precision rate to SAMF. On the other hand, it does decent job in scale estimation. It ranks as $4$th
in AUC. However, it is $20$-$30$ faster than the ones with higher AUC.

\begin{figure}
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=4.00cm]{./figures/Precision_UAV123_10fps.pdf}}
\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Success_UAV123_10fps.pdf}}\\
\end{tabular}
\caption{Evaluation and comparison of the proposed {\it E}nKCF2 tracker on the UAV123$\_$ dataset in terms of the precision and success rates. This dataset consists of temporally downsampled $123$ video sequences captured from a micro UAV.}
\label{fig:UAV123_10fpsDATASET}
\end{figure}
